% !TEX root = ../maturaarbeit.tex
\chapter{Introduction}\label{chap:einleitung}
In this thesis I implement and evaluate an learning algorithm on the task of playing soccer in a simplified simulation environment. Therein I show how computational and mathematical frameworks can be used to produce high quality play, and an aspect of the fundamentals of what is commonly referred to as "AI". For this purpose I introduce the reader to some fundamental concepts of reinforcement learning and how policy gradient based learning methods can be used in conjunction with neural networks to produce seemingly intelligent behaviour. 
\\ I was motivated to pursue this topic by developments in AI which have garnered international attention such as Deep Mind's chess AI AlphaZero, advancements in language processing and recognition, and the ever increasing prevalence of talk about automation through artificial intelligence. Upon investigating what enables and drives these remarkable achievements I discovered the field of machine learning, and one of it's specializations, reinforcement learning. I found this especially appealing because in it, machines learn without human supervision. 
\\ A matura thesis is conducive to, and even requires deep engagement and promotes a solid understanding of the subject chosen as it's focal point. I wanted to gain a deeper understanding of how the systems which may drive our future work, thus in the spring of 2020 I asked my research question: "How can a reinforcement learning algorithm be trained to choose optimal actions in an environment and how can its performance be influenced and improved?". My work is to serve as an answer to just this question by means of example. 